D3064R0: How to Avoid OOTA Without Really Trying

### 2024-02-25 ootavacuous.tex
Move "Illustrative Litmus Tests" to end
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>
Move "Litmus Tests from “Causality Test Cases"" to end
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

The earlier examples shown in
Listings~\ref{lst:Simple Reordering}
and~\ref{lst:Simple OOTA}
can be recast as similar \co{herd7} litmus tests, as shown in
Listing~\ref{lst:Simple Reordering as Litmus Test}
on page~\pageref{lst:Simple Reordering as Litmus Test}
and Listing~\ref{lst:Causality Test Case 4}
on page~\pageref{lst:Causality Test Case 4}, respectively.
Other OOTA-related litmus tests may be found in
Appendix~\ref{app:Litmus Tests from “Causality Test Cases"}
and
Appendix~\ref{app:Illustrative Litmus Tests}.

>>>>

The earlier examples shown in
Listings~\ref{lst:Simple Reordering}
and~\ref{lst:Simple OOTA}
can be recast as similar \co{herd7} litmus tests, as shown in
Listing~\ref{lst:Simple Reordering as Litmus Test}
on page~\pageref{lst:Simple Reordering as Litmus Test}
and Listing~\ref{lst:Causality Test Case 4}
on page~\pageref{lst:Causality Test Case 4}, respectively.
Other OOTA-related litmus tests may be found in
Appendix~\ref{app:Illustrative Litmus Tests}
and
Appendix~\ref{app:Litmus Tests from “Causality Test Cases"}.
